---
title: "t-SNE Visualization of Palmer Penguins"
author: "Afraaz Ali"
date: "2025-03-25"
output: html_document
---
```{r setup, include=FALSE}
library(shiny)
library(Rtsne)
library(ggplot2)
library(palmerpenguins)

# Prepare penguin data
penguin_data <- na.omit(palmerpenguins::penguins[, c("bill_length_mm", "bill_depth_mm", "flipper_length_mm", "body_mass_g")])
```

## t-SNE Visualization of Palmer Penguins

```{r, echo=FALSE}
ui <- fluidPage(
  titlePanel("t-SNE Visualization of Palmer Penguins"),
  sidebarLayout(
    sidebarPanel(
      sliderInput("perplexity", "Perplexity:",
                  min = 5, max = 50, value = 30, step = 1)
    ),
    mainPanel(
      plotOutput("tsnePlot")
    )
  )
)

server <- function(input, output) {
  tsne_result <- reactive({
    set.seed(42)  # Ensure reproducibility
    Rtsne(penguin_data, perplexity = input$perplexity, verbose = FALSE)$Y
  })
  
  output$tsnePlot <- renderPlot({
    tsne_data <- as.data.frame(tsne_result())
    colnames(tsne_data) <- c("Dim1", "Dim2")
    ggplot(tsne_data, aes(x = Dim1, y = Dim2)) +
      geom_point(color = "blue", alpha = 0.7, size = 3) +
      labs(title = paste("t-SNE with Perplexity =", input$perplexity),
           x = "Dimension 1", y = "Dimension 2") +
      theme_minimal()
  })
}

shinyApp(ui = ui, server = server)

